---
title: "Week 02: COVID Visualization Activity"
date: "September, 11 2023"
author: "**`[[`**Lavya Midha**`]]`**"
---

Today, we'll be working with a data set related to COVID.
This data is based on data from the the [COVID Tracking Project](https://covidtracking.com/).
I cleaned up this data and also added total populations from the 2020 for each of the relevant categories.
Note, due to differences in the way race and ethnicity are encoded in the census as compared to the the COVID Tracking Project, the population counts for LatinX may be somewhat inaccurate.

```{r load_data} 
library(tidyverse)
load("CRDT Data.RData")
ls()
```

I've include 4 different data sets.
They all have the same data but have it represented in different ways.
Try using the different data sets and see which ones are good for making which plots.


```{r first_plot}
ggplot(covid_data_count, aes(x = date, y = Cases)) + geom_point()
```



If you want to only look at a specific state, you can do it like this.
For now, see what you can do just using `ggplot`.

```{r}
```


```{r}
covid_data_count |> 
  filter(state == "MA") |> 
  ggplot(aes(x = date, y = Cases, color = race)) + geom_line()
```

1. Write code for a plot and describe what you observe?
The code is for get the cases proportion based on the population if each state per race, The result is a grouped bar chart with different states

```{r}
covid_data_count
ggplot(covid_data_count,aes(y=(Cases/population),x=state,fill=race))+ geom_bar(stat="identity", position=position_dodge())

```
2. Are there any conclusions you can draw?
It is visible that some of the highest proportional cases are shown in people that identify as black. In addition, in almost every state they proportional cases for "other races" same to be high
3. What were you not able to do due to not having the R knowledge?
To be able to get a loop like python that can also print data for each state as separate graphs 
4. What other data would be useful to better understand this data?
I think the data does a pretty good job in explaining what I was aiming at. However, something about the overall structure of distribution of cases in the entire country would have also been great for comparision

